---
title: "Simulation of Trading Strategy Falcon_D"
output: html_notebook
author: Vladimir Zhbanko
date: 20191202
---


#### Fixed parameters

| Variable                 | Value |
|--------------------------|:-----:|
| UseMAFilter              | TRUE  |
| RSI_NoBuyFilter          |   70  |
| RSI_NoSellFilter         |   30  |
| TimeMaxHold              | 28800 |
| Buy_True                 | TRUE  |
| Sell_True                | TRUE  |
| closeAllOnFridays        | FALSE |
| use_market_type          | FALSE |
| IsSizingOn               | TRUE  |
| Risk                     | 1     |
| MaxPositionsAllowed      | 10    |
| UseFixedStopLoss         | TRUE  |
| FixedStopLoss            | 300   |
| IsVolatilityStopOn       | TRUE  |
| VolBasedTPMultiplier     | 12    |
| UseFixedTakeProfit       | FALSE |
| IsVolatilityTakeProfitOn | TRUE  |
| VolBasedTPMultiplier     | 6     |
| atr_period               | 15    |

#### Parameters to optimize

Only optimize following parameters:

|   Variable  | Start | Step | Stop |
|:-----------:|-------|------|------|
|  StartHour  | 3     | 1    | 23   |
| MinPipLimit | 5     | 5    | 50   |


#### Optimization restrictions

Maximal drawdown 15%

#### Parameters criteria selection

Following criterias must be true:

* Profit factor > 2
* Number of trades during simulation > 30
* More than 10 good sets are present in the simulation results (with profit factor > 2)

Select the top set with maximum profit, maximum number of trades

#### When we skip simulation?

Whenever parameters criteria selection are not true then:

* skip ths set of parameters
* change start/end dates of simulations

### Simulation

#### File cleanup

before simulation:

* change `From:` and `To:` dates in the Strategy Tester (Increase by *4* month value in field `From:`; Increase by *2* month value in the field `To:`)
* delete file `OrdersResultsT2.csv` from the folder `C:\Program Files (x86)\FxPro - Terminal2\tester\files`
* if not done, create a folder for specific currency pair e.g.: `~\SIM\EURUSD`

#### Perform Simulation

* Insure folder `C:\Program Files (x86)\FxPro - Terminal2\tester\files` is empty or it does not contain file `OrdersResultsT2.csv`
* Press button `Start` to initiate trades simulation

Optional: check tab `Graph` of Strategy Tester to evaluate distribution of trade results

#### Transfer of file to the collection folder

right after simulation:

* transfer file `OrdersResultsT2.csv` to the folder `~\SIM\******`
* rename the file to reflect optimization round (e.g. `1.csv` see table below)

**Note: sometimes there would be no file, then continue rename files to maintain consecutive names**

See below table with examples:

| Pair   | Round | FileName | FolderLocation |
|--------|-------|----------|----------------|
| USDCHF | 1     | 1.csv    | SIM/USDCHF'    |
| USDCHF | 2     | 2.csv    | SIM/USDCHF'    |
| USDCHF | 3     | no file  | SIM/USDCHF'    |
| USDCHF | 4     | no file  | SIM/USDCHF'    |
| USDCHF | 5     | 5.csv    | SIM/USDCHF'    |
| USDCHF | 6     | 6.csv    | SIM/USDCHF'    |
| USDCHF | 7     | 7.csv    | SIM/USDCHF'    |
| EURUSD | 1     | 1.csv    | SIM/GBPUSD'    |
| EURUSD | 2     | 2.csv    | SIM/GBPUSD'    |
| EURUSD | 3     | 3.csv    | SIM/GBPUSD'    |
| EURUSD | 4     | 4.csv    | SIM/GBPUSD'    |
| EURUSD | 5     | 5.csv    | SIM/GBPUSD'    |
| EURUSD | 6     | 6.csv    | SIM/GBPUSD'    |
| EURUSD | 7     | 7.csv    | SIM/GBPUSD'    |


#### Going to next optimization cycle after Simulation

Do the following:

* Check box `Optimization`
* Reduce value `Month` of the Strategy Tester field `From:` by 2
* Press button `Start` to initiate new Optimization

### Data Aggregation

Once the files are in the right folders use following code to aggregate data

```{r message=FALSE, warning=FALSE}
library(lazytrade)
library(lubridate)
library(tidyverse)

# folders with results //change this path//
DFOLDER <- "C:/Users/fxtrams/Documents/000_TradingRepo/FALCON_D/TS"

DFR <- opt_aggregate_results(DFOLDER)

```


### Visualize data

```{r message=FALSE, warning=FALSE}
# visual way
opt_create_graphs(DFR, graph_type = 'ts')

```

```{r message=FALSE, warning=FALSE}
# visual way
opt_create_graphs(DFR, graph_type = 'bars')

```

#### Save both graphs to pdf file

```{r message=FALSE, warning=FALSE}
# graphs in pdf
opt_create_graphs(DFR,outp_path = getwd())

```


### Analyse the results

#### Any Pair is better?

```{r}
DFR %>% 
  group_by(Symbol) %>% 
  summarise(PairGain = sum(Profit))
```


#### Any Pair/Direction is better?

```{r}
DFR %>% 
  group_by(Symbol, OrderType) %>% 
  summarise(PairGain = sum(Profit))
```